---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
devtools::load_all()
rttedata <- readr::read_csv(system.file('extdata/DAT-1c-RED-1a-PMX-WOWTTE-PFPMX-1.csv', package= 'PMXtte'), show_col_types = FALSE)
rttedata <- dplyr::filter(rttedata, EVID == 0, TYPE == 2)

```
# PMXtte
Support functions for (Repeated) Time-To-Event data analysis. Generate summary tables and Kaplan-Meier plot for the exploratory analyses, and visual predictive checks for model evaluation. 

## Installation
You can install the development version of PMXtte from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("pharmetheus/PMXtte")
```
To get the latest stable release (including vignettes), please click the appropriate link on the right side of the page. Download the file with a name that starts with PMXtte. Install PMXtte with the `install.packages` command, e.g.:

```{r,eval=FALSE}
install.packages("path_to_release.tar.gz")
```

```{r, fig.height=7}
tte1data <- rttedata %>% filter_xth_event(1)
tte1data$TRTF <- factor(paste(tte1data$TRTN, "mg"), levels = paste(sort(unique(tte1data$TRTN)), "mg"))
ggKAP(
  tte1data,
  time_var = "TSFDD", 
  color_var = "TRTF", 
  label_color = "Treatment"
)
```


