---
title: "ggKAP"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ggKAP}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(PMXtte)
library(magrittr)
```

Time to event data can be visualized thanks to the `ggKAP()` function. After importing the data, you can generate a standard plot with the following command:

```{r}
rttedata <- readr::read_csv(system.file('extdata/DAT-1c-RED-1a-PMX-WOWTTE-PFPMX-1.csv', package= 'PMXtte'), show_col_types = FALSE)
rttedata <- dplyr::filter(rttedata, EVID == 0, TYPE == 2)

# Load observed data
odata <- rttedata %>%
  filter_xth_event(1)

ggKAP(odata, time_var = "TSFDW", dv_var = "DV")

```

This output is composed of several parts arranged together, notably a risk table in the bottom and a figure in the middle, the latter contains a Kaplan-Meier curve, censoring events and a parametric confidence interval. It will also include the median survival curve if this is achieved. All these elements are described in a dedicated legend on the top. All these elements can be removed/added with the `show_*` arguments, e.g.:


```{r}
ggKAP(
  odata, 
  time_var = "TSFDW", dv_var = "DV", 
  show_kpm = TRUE, 
  show_censor = TRUE, 
  show_risktable = FALSE, 
  show_median = FALSE,
  show_se = FALSE
  )
```


It is possible to stratify the data, using different colors and facetting. Note that, for coloring, the variable should preferably be a factor, alternatively a character string or a logical, but not a numeric (double or integer) (you would get an error).

```{r}
odata$DOSEF <- as.factor(odata$DOSEN)
ggKAP(
  odata, 
  time_var = "TSFDW", dv_var = "DV", 
  color_var = "DOSEF", facet_var = "STUDYIDN", 
  )
```


One can see that coloring variable automatically does a log-rank test between the groups in each panel of the figure. This can be shown/removed with the `show_pval` argument.


Now, let's add simulated data.
```{r}
sdata <- readRDS(system.file('extdata/vpcdat.rds', package= 'PMXtte')) %>%
  filter_xth_event(1)
sdata$TSFDW <- sdata$TIME / (24*7)
sdata$DOSEF <- as.factor(sdata$DOSE)
sdata$SEXN <- as.factor(sdata$SEX)


```







